\documentclass[11pt, letterpaper]{article}

% --- Packages and settings ---
\usepackage[
    ignoreheadfoot,
    top=1.5cm,
    bottom=1.5cm,
    left=1.5cm,
    right=1.5cm,
    footskip=0.5cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Hongru Ma's CV},
    pdfauthor={Hongru Ma},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}
\usepackage[scaled=0.92]{helvet}

\raggedright
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\Large\sffamily}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10cm,
        parsep=0.10cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0cm}{0cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
}

\begin{document}

% --- HEADER ---
\begin{header}
    \fontsize{24pt}{24pt}\selectfont Hongru Ma

    \vspace{5pt}

    \normalsize
    \kern 2.0pt%
    \mbox{\href{mailto:mahongru.dev@gmail.com}{mahongru.dev@gmail.com}}%
    \kern 2.0pt%
    |%
    \kern 2.0pt%
    \mbox{\href{https://www.linkedin.com/in/mahongru/}{LinkedIn}}%
    |%
    \kern 2.0pt%
    \mbox{\href{https://github.com/mahongru}{GitHub}}%
    \kern 2.0pt%

\end{header}

\vspace{0.3cm}

% --- SUMMARY ---
\section{Summary}
\vspace{0.1cm}
Experienced in building and scaling cross-platform products, delivering high-quality mobile and cloud systems. Focused on maintainability, performance, technical direction, and collaboration to create thoughtful, user-centered experiences.
\vspace{0.1cm}

% --- EXPERIENCE ---
\section{Work Experience}

\textbf{Engineering Manager}, Intella — Cairo, Egypt \hfill 2025 – Present
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Set technical direction, balance delivery with technical quality, and guide architectural decisions.
        \item Partner with product, design, and backend teams to align roadmap, scope, and execution.
        \item Coach engineers through regular feedback, career development, and performance reviews.
    \end{highlights}
\end{onecolentry}

\vspace{0.3cm}

\textbf{Software Engineer}, Delfina Care — California, US \hfill 2022 – 2025
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Built and maintained the next generation of digital pregnancy care via a robust Flutter mobile app.
        \item Designed scalable features using modular components and BLoC state management.
        \item Implemented deferred deep linking to streamline onboarding and boost user retention.
        \item Collaborated with backend and design teams to refine UX and ensure cross-platform consistency.
    \end{highlights}
\end{onecolentry}

\vspace{0.3cm}

\textbf{Software Engineer}, Explore Agora — Cairo, Egypt \hfill 2020 – 2022
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Developed mobile learning applications that delivered engaging, interactive education experiences.
        \item Architected reusable Flutter modules, improving scalability and reducing maintenance overhead.
        \item Mentored junior engineers and led code reviews to ensure consistent development standards.
    \end{highlights}
\end{onecolentry}

\vspace{0.3cm}

\textbf{Software Engineer}, Rival Technologies — Vancouver, BC \hfill 2018 – 2019
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Built and maintained cloud services on GCP with high reliability and scalability.
        \item Developed automated testing pipelines and integrated CI/CD workflows to accelerate releases.
        \item Supported onboarding and strengthened team development processes.
    \end{highlights}
\end{onecolentry}

\vspace{0.3cm}

\textbf{Software Developer}, OpenLanguage — Vancouver, BC \hfill 2017
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Implemented new features for a language-learning platform using modern web technologies.
        \item Optimized database queries and improved application performance.
    \end{highlights}
\end{onecolentry}

% --- LEADERSHIP ---
\section{Leadership}
\vspace{0.1cm}
\begin{onecolentry}
    \begin{highlights}
        \item Led architecture reviews and cross-team technical discussions to align engineering direction.
        \item Guided developers in improving technical proficiency and software design quality.
        \item Promoted scalable architecture and robust testing to ensure long-term reliability.
        \item Enhanced onboarding and documentation to accelerate developer productivity.
    \end{highlights}
\end{onecolentry}

% --- EDUCATION ---
\section{Education}
\vspace{0.1cm}
\begin{twocolentry}{2016}
    \textbf{Diploma in Web Development}, Lighthouse Labs
\end{twocolentry}

\begin{twocolentry}{2010}
    \textbf{B.Sc. in General Management}, German University in Cairo
\end{twocolentry}

\end{document}
